Using cosmic variance to constrain the dark matter halo mass and occupation fraction of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-06-24 paper/ms.tex
advances

\newcommand{\kms}{\,km~s$^{-1}$}
\def\squig{\sim\!\!}
\newcommand{\LCDM}{$\Lambda$CDM~}
\newcommand{\beq}{\begin{eqnarray}}  
\newcommand{\eeq}{\end{eqnarray}}   
\newcommand{\zz}{$z\sim 3$} 
\newcommand{\avg}[1]{\langle{#1}\rangle}  
\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha}\else{Ly$\alpha$}\fi}}
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc }\fi}}  
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}  
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\lya}{{Lyman$\alpha$~}}
\newcommand{\clara}{{\texttt{CLARA}}~}
\newcommand{\rand}{{\ifmmode{{\mathcal{R}}}\else{${\mathcal{R}}$ }\fi}}  
\newcommand{\Lsun}{\mbox{\,$L_{\odot}$}}
\newcommand{\like}{\mathscr{L}}
\newcommand{\bftheta}{\mathbf{\Theta}}
\newcommand{\degree}{\ensuremath{^\circ}}
\def\spose#1{\hbox to 0pt{#1\hss}}
\def\simlt{\mathrel{\spose{\lower 3pt\hbox{$\mathchar"218$}}
     \raise 2.0pt\hbox{$\mathchar"13C$}}}
\def\simgt{\mathrel{\spose{\lower 3pt\hbox{$\mathchar"218$}}
     \raise 2.0pt\hbox{$\mathchar"13E$}}}
\font\smcap=cmcsc10

@@

\begin{abstract}
We use cosmological N-body dark matter only simulations to constrain the
characteristic mass of dark matter halos hosting Lyman-Alpha Emitting
(LAE) galaxies at a redshift of $z=3.1$. The method is based on
matching the statistics for the number density between mock and
observed fields. The mock fields are constructed using a simple model
where a dark matter halo can only host one LAE with a probability
$f_{\rm occ}$ if its mass is found withing a certain range mass range
delimited by two threshold values, $M_{\rm min}$ and $M_{\rm max}$. 
We also maximize the number of mocks surveys consistent with
observations and impose consistency with the angular correlation
function. Under these conditions we find that LAEs are preferentially
hosted by halos in very narrow mass ranges less than 0.5 dex in width,
with the minimum mass $10\leq \log_{10}M_{\rm min}\leq 10.9$ and the
occupation fraction $f_{\rm   occ}\leq 0.2$.  Our finding suggest that
the most massive dark matter halos at that epoch do not host the
brightest LAEs. This also gives support to observational evidence that
says that only a small fraction of star forming galaxies can be
actually detected as LAEs.
\end{abstract}

@@

We find that the majority ($70\%$) of the best models have a low
ocacupation fraction $f_{\rm occ}\leq 0.3$. This preference goes in
the same direction as the observational constraint on $f_{\rm occ}\sim
0.1-0.2$ derived at $z=2.2$ by \cite{Hayes2010} and recent theoretical
study of observational data in a wide redshift range $0<z<6$ by
\cite{Dijkstra2013}.

The observational estimation by \cite{Hayes2012} was based on blind
surveys of the H$\alpha$ and Lyman $\alpha$ line. Using corrections by
extinction to obtain an estimate for the intrinsic H$\alpha$
luminosity, and using values for the theoretical expectation of the
ratio Lyman$\alpha$/H$\alpha$ they derive an bulk escape fraction for
the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
  esc}=(10.7\pm 2.8)\%$ if a different dust correction is used.

@@

The results by \cite{Dijkstra2013} use a similar principle. They
compared observationally dereived star formation functions to LAE
luminosity functions. At $z\sim 3.0$ they derive an affective escape
fraction of $f_{\rm esc}=(17\pm 5)\%$, which in turn using the same
arguments in \cite{Hayes2010} could be interpreted as an occupation
fraction $f_{\rm occ}\sim 0.2$.  We consider a sucess of our method
the fact that we find that most of the consistent models show a low
occupation fraction.

The study of the escape farction is also complementary to the size of
the halo mass range $\Delta M=\log_{10}M_{\rm max} - \log M_{\rm
  min}$for LAEs. All the successful model we have found can be 
split into three families. 
\begin{itemize}
\item[(1)] Low $f_{\rm occ}\leq 0.3$ and low $\Delta M\leq 1.0$
  dex: 24 models.
\item[(2)] High $f_{\rm occ}> 0.3$ and low $\Delta M\leq 1.0$: 14 models
\item[(3)] Low $f_{\rm occ}\leq 0.3$ and high $\Delta M > 1.0$dex: 11
  models
\end{itemize}

There is a clear majority of models with a narrow $\Delta M\leq
1$, such models imply that there is a cut for lower and higher halo masses
that render inefficient the presence and/or detection of LAEs.  A cut
a lower masses can be readily interepreted in terms of the minimal halo star
formation rate needed to produce the necessary \lya luminosity to be
above a given detection threshold.

The cut at higher halo masses requires a different explanation. A
possible interpretation can be made in terms of a lower escape
fraction of \ly radiation in massive systems. There are detailed models for
radiative transfer that support the idea that massive galaxies with
higher metallicities have larger dust contents than lower mass
systems, which due to the resonant nature of the \ly line are enough
to produce high absorption of \ly photons but not of continuum or
other non-resonant lines.

This preference for narrow $\Delta M$ ranges for hosting LAEs together
with the total absence of reasonable models with $M_{\rm max}>
10^{12}$\hMsun shows that our models supports theoretical insights
where the most massive systems are not bright \ly sources.

%The first, where the range $M_{\rm min}-M_{\rm max}$ is narrow,
%typically of less than $<1.0$ dex. While in the second familiy th
%extent $>1.0$ dex. In the first case the minimum halo mass is found to
%be in a wide range $10^{10}\hMsun <M_{\rm min}< 10^{11.5}\hMsun$ while
%in the second case, only models with $M_{\rm min}\sim 10^{10.9}\hMsun$
%are compatible with the observational contraints. In what follows we
%discuss the implications of the existence of these two families of
%models.  
%When we additional include the ACF constraint we find that only models with 
%$\log_{10}M_{\rm min}\leq 11.0$ and $\log_{10}M_{\rm max}\leq 12.0$ 
%are now consistent with observations.

%Including all the observational constraints we find that only between $15$ to $20$ 
%models reproduces observations. The list for the model parameters is in the
%Appendix in Table \ref{table:models_match}.

\subsection{In the context of abundance matching models}

Using abundance matching methods throughout cosmic time from redshifts
$0<z<8$ \cite{Behroozi2013a,Behroozi2013b} report that the instantaneous star
formation efficiency (star formation rate divided by the stellar mass)
presents a clear maximum around $10^{11.7}$\Msun at all redshifts
$z<4$.

This mass scale is strictly superior to the all the $M_{\rm max}$
values allowed in the consistent models. Using the results published
in \cite{Behroozi2013a} we find that the typical stellar mass in halos
of $10^{11.4}$\hMsun is $(1.0\pm0.3)\times 10^{9.0}$ \hMsun, while
their star formion rate is in the range $0.6\pm 0.2$ Msun
yr$^{-1}$.  This halo mass range around $10^{11.4}$ \hMsun is the
lower bound of what is computed in the abundance matching model in
order to fit the observational data for the stellar mass function
based on the obervations of Lyman Break Galaxies.

We have the opposite situation in the second familiy of models. If
we have a wide range in halo masses, where the upper end of the halo
masses can be considered as observed LAEs, one can expect that bright
LBGs will have a correspondence as observed LAEs. The most interesting
aspect is that there is a clear cut in the minimal mass that can be
attained by observed LAEs $M_{\rm min}> 10^{11}$\hMsun. This puts a tight
constraint on the relationship between the minimum star formation rate
required to be observed as a LAE and this minimal halo mass.

%... Intrinsic emission and escape fraction.

%... Star formation rate efficiency at this redshift.

%... Mass dependence of the escape fraction.

%... Discuss all this in terms of the star formation efficiency in
Behroozi et al.

\subsection{Implications for large LAEs surveys}

... The bias for the preferred halo mass.

... The scale at which cosmic variance drops.

... This can be observationally tested with HETDEX.

@@

\section{Conclusions}
In this \documentname we constrain the preferred mass for dark matter
halos hosting Lyman Alpha Emitters at a redshift $z=3.1$. We use a
method that matches the cosmic variance in the surface
density number of LAEs between mock and real observations. The mock
catalogs are based on a simplified model with three basic parameters: the halo
mass range where LAEs can be found, $M_{\rm   min}<M_{\rm h}<M_{\rm
  max}$, and the fraction of the halos in thisrange that are actully
occupied, $f_{\rm occ}$. After a thorugh exploration of the parameter
space we are able to constrain the mass range of dark matter halos
hosting LAEs to be in the range $<M_{\rm   h}<$ and a corresponding
occupation fraction that escales as $f_{\rm   occ} = M_{\rm min}$.

We use three additional constraints to reduce the allowed
range of models. The first imposes a tighter criterion to consider a
model succesful, namely that all the mock surveys for a given model
must be consistent with observations. This restriction narrows down
the allowed range of models to be.

The second constraint is based on the observational results that high
redshift LAEs have a bulk Lyman alpha escape fraction of $XX$ which
can be also interepreted as an average occupation fraction of $XX$.

Including additional observational constraints on the occupation
fraction allows us to reduce the range of allowed halo masses to be in
a narrower range of $<M_{\rm h}<$. Including the information from the
angular correlation function (ACF) does not allows us to impose
further constraints. This is due to the scatter in the ACF due to the
cosmic variance on the field observed by XXX

We simulation allows us to extract $210$ sub-boxes each of which has a
comparable volume to the individual fields of view observed by
\cite{Yamada2012}. The comparison of the observed number density
distribution against the results from our model is based on three
different ways of constructing mock surveys. The first reproduces the
spatial correlation between the $12$ observational fields ({\texttt
  match}), the second breaks this spatial correlation while keeping
the number of fields ({\texttt random}) and the third one simply
includes all the $210$ sub-boxes ({\texttt full}). We find that the
methods {\texttt match} and {\texttt random} allow a larger set of
models than the {{\texttt random}} method. We do not find a
significant difference between the two first methods.

@@

\begin{table}
\begin{center}
\begin{tabular}{ccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$\\\hline
10.1& 10.2& 0.1\\
10.3& 10.5& 0.1\\
10.4& 10.7& 0.1\\
10.5& 10.9& 0.1\\
10.5& 11.0& 0.1\\
10.6& 11.2& 0.1\\
10.6& 11.3& 0.1\\
10.6& 11.4& 0.1\\
10.6& 11.5& 0.1\\
10.6& 11.6& 0.1\\
10.6& 11.7& 0.1\\
10.6& 10.8& 0.2\\
10.7& 11.0& 0.2\\
10.8& 11.2& 0.2\\
10.8& 11.3& 0.2\\
10.8& 11.4& 0.2\\
10.9& 11.7& 0.2\\
10.9& 11.8& 0.2\\
10.9& 11.9& 0.2\\
%10.9& 12.0& 0.2\\
%10.9& 12.1& 0.2\\
%10.9& 12.2& 0.2\\
%10.9& 12.3& 0.2\\
%10.9& 12.4& 0.2\\
%10.9& 12.5& 0.2\\
%10.9& 12.6& 0.2\\
%10.9& 12.7& 0.2\\
%10.9& 12.8& 0.2\\
%10.9& 12.9& 0.2\\
%10.9& 13.0& 0.2\\\hline\hline
\end{tabular}
\end{center}
\caption{List of model parameters for the best models that have all
  mock surveys consistent with observations and an occupation
  fraction $f_{\rm occ}\leq 0.2$. This corresponds to the {\texttt
    match} method to construct the mock surveys. \label{table:models_match}. }
\end{table}

>>>>

\newcommand{\kms}{\,km~s$^{-1}$}
\def\squig{\sim\!\!}
\newcommand{\LCDM}{$\Lambda$CDM~}
\newcommand{\beq}{\begin{eqnarray}}  
\newcommand{\eeq}{\end{eqnarray}}   
\newcommand{\zz}{$z\sim 3$} 
\newcommand{\avg}[1]{\langle{#1}\rangle}  
\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha}\else{Ly$\alpha$~}\fi}}
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc }\fi}}  
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}  
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\lya}{{Lyman$\alpha$~}}
\newcommand{\clara}{{\texttt{CLARA}}~}
\newcommand{\rand}{{\ifmmode{{\mathcal{R}}}\else{${\mathcal{R}}$ }\fi}}  
\newcommand{\Lsun}{\mbox{\,$L_{\odot}$}}
\newcommand{\like}{\mathscr{L}}
\newcommand{\bftheta}{\mathbf{\Theta}}
\newcommand{\degree}{\ensuremath{^\circ}}
\def\spose#1{\hbox to 0pt{#1\hss}}
\def\simlt{\mathrel{\spose{\lower 3pt\hbox{$\mathchar"218$}}
     \raise 2.0pt\hbox{$\mathchar"13C$}}}
\def\simgt{\mathrel{\spose{\lower 3pt\hbox{$\mathchar"218$}}
     \raise 2.0pt\hbox{$\mathchar"13E$}}}
\font\smcap=cmcsc10

@@

\begin{abstract}
We use cosmological N-body dark matter only simulations to constrain the
characteristic mass of dark matter halos hosting Lyman-Alpha Emitting
(LAE) galaxies at a redshift of $z=3.1$. The method is based on
matching the statistics for the number density between mock and
observed fields. The mock fields are constructed using a simple model
where a dark matter halo can only host one LAE with a probability
$f_{\rm occ}$ if its mass is found withing a certain range mass range
delimited by two threshold values, $M_{\rm min}$ and $M_{\rm max}$. 
We also maximize the number of mocks surveys consistent with
Our most important results is that, unlike previous studies, a pure
clustering analysis cannot fully constraint the halo occupation
fraction for LAEs.

Most of the models have a narrow mass range $\Delta M \equiv
\log_{10}M_{\rm max} - \log_{10} M_{\rm min}< 1.0$ dex and a low
occupation fraction $f_{\rm occ}\leq 0.3$.

observations and impose consistency with the angular correlation
function. Under these conditions we find that LAEs are preferentially
hosted by halos in very narrow mass ranges less than 0.5 dex in width,
with the minimum mass $10\leq \log_{10}M_{\rm min}\leq 10.9$ and the
occupation fraction $f_{\rm   occ}\leq 0.2$.  Our finding suggest that
the most massive dark matter halos at that epoch do not host the
brightest LAEs. This also gives support to observational evidence that
says that only a small fraction of star forming galaxies can be
actually detected as LAEs.
\end{abstract}

@@

We find that $70\%$ of the best models have a low
ocacupation fraction $f_{\rm occ}\leq 0.3$. This preference goes in
the same direction as the observational constraint on $f_{\rm occ}\sim
0.1-0.2$ derived at $z=2.2$ by \cite{Hayes2010} and recent theoretical
study of observational data in a wide redshift range $0<z<6$ 
\citep{Dijkstra2013}.

The observational estimation by \cite{Hayes2010} was based on blind
surveys of the H$\alpha$ and Lyman $\alpha$ line. Using corrections by
extinction to obtain an estimate for the intrinsic H$\alpha$
luminosity, and using values for the theoretical expectation of the
ratio Lyman$\alpha$/H$\alpha$ they derive an bulk escape fraction for
the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
  esc}=(10.7\pm 2.8)\%$ if a different dust correction is used.

@@

\cite{Dijkstra2013} use a similar principle to derive their results. They
compared observationally derived star formation functions to LAE
luminosity functions. At $z\sim 3.0$ they derive an affective escape
fraction of $f_{\rm esc}=(17\pm 5)\%$ could be interpreted as an
occupation fraction $f_{\rm occ}\sim 0.2$.  We consider a sucess of
our method the fact that we find that most of the consistent models
show a low occupation fraction.

A complementary perspective to the range of the allowed values for the
escape fraction is the quantification of the allowed halo mass range
$\Delta M=\log_{10}M_{\rm max} - \log M_{\rm  min}$for LAEs. In this
respect, we find that all the successful models can be  split into
three families:

\begin{itemize}
\item[(1)] Low $f_{\rm occ}\leq 0.3$ and low $\Delta M\leq 1.0$
  dex: 24 models.
\item[(2)] Low $f_{\rm occ}\leq 0.3$ and high $\Delta M > 1.0$dex: 11
  models
\item[(3)] High $f_{\rm occ}> 0.3$ and low $\Delta M\leq 1.0$: 14 models
\end{itemize}

There is a clear majority of models with a narrow $\Delta M\leq
1$. Such models imply that there is a cut for lower and higher halo masses
that render inefficient the presence and/or detection of LAEs.  A cut
at the low mass end can be readily interepreted in terms of the minimal halo star
formation rate needed to produce the necessary \lya luminosity to be
above a given detection threshold.  However, under the reasonable assumption of star formation rate
increainsng with halo mass, the cut at higher halo masses requires a
different explanation.

A possible interpretation can be made in terms of a drecreasing escape
fraction of \ly radiation in massive systems. There are detailed models for
radiative transfer that support the idea that massive galaxies with
higher metallicities have larger dust contents than lower mass
systems, which due to the resonant nature of the \ly line are enough
to produce high absorption of \ly photons but not of continuum or
other non-resonant lines.

This preference for narrow $\Delta M$ ranges for hosting LAEs together
with the total absence of reasonable models with $M_{\rm max}>
10^{12}$\hMsun shows that our models supports theoretical insights
where the most massive systems are not bright \ly sources \citep{ForeroRomero2012}.

\subsection{Comparison to other clustering estimates}

Since the observational estimates based on the ACF infered from photometric
measurements in the Extended Chandra Deep Field South
\citep{Gawiser07} it is a well accepted fact that the median dark
matter masses of halos hosting LAEs is $\log_{10}M_{\rm
  med}=10.9^{+0.5}_{-0.9}$\Msun, with a corresponding occupation
fraction of $1-10\%$.  Our results are in a good agrement with those estimates for the
host mass. This is not unexepected given that we have also
required consistency with ACF measurements.

The novelty in our approach is that we have a detailed estimate for 
host halo mass range. Following the numbers shown for the three
families in the previous section, we see that two thirds of the best models
have a narrow mass range, less than $<1.0$ dex, out of the $2.5$ dex
spanned by dark matter halos at that redshift. Only one fourth of the
models indicate a wide mass range with $>1.0$dex.

As a byproduct of our results, we are now able to demonstrate that a
simple clustering analysis is not enough to rule out models with a
high occupation fraction $f_{\rm occ}>0.3$, they represent almost
one fourth of our best models, coinciding with a wide range in halo
masses $\Delta M>1.0$ dex.

%\subsection{In the context of abundance matching models}

%Using abundance matching methods throughout cosmic time from redshifts
%$0<z<8$ \cite{Behroozi2013a,Behroozi2013b} report that the instantaneous star
%formation efficiency (star formation rate divided by the stellar mass)
%presents a clear maximum around $10^{11.7}$\Msun at all redshifts
%$z<4$.

%This mass scale is strictly superior to the all the $M_{\rm max}$
%values allowed in the consistent models. Using the results published
%in \cite{Behroozi2013a} we find that the typical stellar mass in halos
%of $10^{11.4}$\hMsun is $(1.0\pm0.3)\times 10^{9.0}$ \hMsun, while
%their star formation rate is in the range $0.6\pm 0.2$ Msun
%yr$^{-1}$.  This halo mass range around $10^{11.4}$ \hMsun is the
%lower bound of what is computed in the abundance matching model in
%order to fit the observational data for the stellar mass function
%based on the obervations of Lyman Break Galaxies.

%Most of the prefered models have a halo mass range with $M_{\rm
%  max}<10^{11.4}$\hMsun. This suggests that a detailed and careful
%study of the spectral properties of LAEs coupled to the kind of
%analysis performed in this paper can be a guide in the study of the
%properties of low mass dark matter halos at $z=3.1$, extending the
%capabilities of abundance matching methods.

%we have a wide range in halo masses, where the upper end of the halo
%masses can be considered as observed LAEs, one can expect that bright
%LBGs will have a correspondence as observed LAEs. The most interesting
%aspect is that there is a clear cut in the minimal mass that can be
%attained by observed LAEs $M_{\rm min}> 10^{11}$\hMsun. This puts a tight
%constraint on the relationship between the minimum star formation rate
%required to be observed as a LAE and this minimal halo mass.

@@

\section{Conclusions}

In this \documentname we constrain the preferred dark matter mass
and occupation fraction for halos hosting Lyman Alpha Emitters at
redshift $z=3.1$. We use a method that matches the cosmic variance in the surface
density number of LAEs between mock and real observations and provides
consistent results with observational estimates for the angular
correlation function. The mock catalogs are based on a simplified
model with three basic parameters: the halo mass range where LAEs can
be found, $M_{\rm   min}<M_{\rm h}<M_{\rm   max}$, and the fraction of
the halos in this range that are actully occupied, $f_{\rm occ}$. After
a thorough exploration of the parameter space we find that wide
variety of models are consistent with the observational constraints,
where only a minority has been considered so far in the
literature. Out of $9000$ initial combinations for the model
parameters we end up with $49$ sucessful arrangement of parameters.

These parameter sets can be split into three families depending the mass range
$\Delta M=\log_{10}M_{\rm max} - \log_{10}M_{\rm min}$ and the
occupation fraction $f_{\rm occ}$. The first family is narrow both in
$\Delta M$ and $f_{\rm occ}$, a second familiy is only narrow in
$\Delta M$ and the third is only narrow in $f_{\rm occ}$.

Analysis based in observations have been only able to describe models
in the third family, but have so far missed the possibility of the first
two: a narrow mass range and any value for the escape fraction.

Many different observational estimates on the occupation fraction of
LAEs at $z=3$ suggest that the occupation fraction must be low $f_{\rm
  occ}<0.2$. We find that the first and most numerous family of models
is consistent with this suggestion, where also a narrow range for the
halo mass $\Delta M<1.0$ is prefered.

@@

\begin{table}
\begin{center}
\begin{tabular}{ccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$\\\hline
10.1& 10.2& 0.1\\
10.3& 10.5& 0.1\\
10.4& 10.7& 0.1\\
10.5& 10.6& 0.3\\
10.5& 10.9& 0.1\\
10.5& 11.0& 0.1\\
10.6& 10.8& 0.2\\
10.6& 11.2& 0.1\\
10.6& 11.3& 0.1\\
10.6& 11.4& 0.1\\
10.6& 11.5& 0.1\\
10.6& 11.6& 0.1\\
10.7& 11.0& 0.2\\
10.8& 11.2& 0.2\\
10.8& 11.3& 0.2\\
10.8& 11.4& 0.2\\
10.9& 11.3& 0.3\\
10.9& 11.7& 0.2\\
10.9& 11.8& 0.2\\
10.9& 11.9& 0.2\\
11.0& 11.6& 0.3\\
11.0& 11.7& 0.3\\
11.0& 11.8& 0.3\\
11.0& 12.0& 0.3\\\hline\hline
\end{tabular}
\end{center}
\caption{\label{table:thirdfamily}List of parameters for the first family of models. Narrow
  mass range $\Delta M\leq 1.0$dex and low occupation fraction $f_{\rm occ}\leq 0.3$.}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{ccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$\\\hline
10.6& 10.7& 0.4\\
10.7& 10.8& 0.5\\
10.8& 10.9& 0.6\\
10.8& 11.0& 0.4\\
10.9& 11.0& 0.8\\
10.9& 11.0& 0.9\\
10.9& 11.1& 0.5\\
11.0& 11.1& 1.0\\
11.0& 11.4& 0.4\\
11.1& 11.3& 0.7\\
11.1& 11.7& 0.4\\
11.2& 11.5& 0.7\\
11.2& 11.6& 0.6\\
11.2& 11.9& 0.5\\\hline\hline
\end{tabular}
\end{center}
\caption{\label{table:secondfamily}List of parameters for the second family of models. Narrow
  mass range $\Delta M\leq 1.0$dex and high occupation fraction $f_{\rm occ}>0.3$.}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{ccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$\\\hline
10.6& 11.7& 0.1\\
10.9& 12.1& 0.2\\
10.9& 12.2& 0.2\\
10.9& 12.3& 0.2\\
10.9& 12.4& 0.2\\
10.9& 12.5& 0.2\\
10.9& 12.6& 0.2\\
10.9& 12.7& 0.2\\
10.9& 12.8& 0.2\\
10.9& 12.9& 0.2\\
10.9& 13.&0 0.2\\\hline\hline
\end{tabular}
\end{center}
\caption{\label{table:thirdfamily}List of parameters for the third family of models. Broad
  mass range $\Delta M >1.0$dex and low occupation fraction $f_{\rm occ}\leq0.3$.}
\end{table}
